---
title: "Datamining"
output: html_document
---

```{r}
install.packages()
```

# Datamining 

## 지도학습 - Prediction, Estimation  

Prediction - Linear Regression, Regression Tree, Model Tree, SVM(Support Vector Machine), Neural Network, Deep Learning, ARIMA, Exponential smoothing

Estimation - Decision Tree, Logistic Regression, Discriminant Analysis, k-NN(k-Nearest neighbor), CBR(Case-Based Reasoning), Naive Bayes Classification, SVM, Neural Network, Ensemble(Bagging, Boosting, Random Forest)

## 비지도학습 - Pattern,Rule, Groupingm, Dimension Reduction, Video, Image, Text, Signal processing 

Pattern, Rule - Association Rule Analysis, Sequence Analysis, Network Analysis, Link Analysis, Graph theory, Structural Equation Modeling, Path Analysis 

Grouping - k-Means Clustring, Fuzzy Clustring, SOM(self-Organizing Map)

Dimension Resduction - PCA, Factor Analysis, SVD 

video, Image, Text, Singnal processing - Wavelet/fast fourier Transformation, DTW, SAX, Line/Circular Hough Transformation, Text mining, Sentiment Analysis  
 
```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
